Making Sense of Tweets: Student research projects in data science

### 2019-09-08 Rmd/jse-2019-ms.Rmd
updated bib

---
title: 'Making Sense of Tweets: Student research projects in data science'
author: "Frederick J. Boehm and Bret M. Hanlon"
date: "8/20/2019"
output: html_document
---

>>>>

---
title: 'Making Sense of Tweets: Student research projects in data science'
author: "Frederick J. Boehm and Bret M. Hanlon"
date: "8/20/2019"
lastmod: "`r lubridate::now()`"
bibliography: jse.bib
output: html_document
---

## Introduction

## Methods

- how did we/they conceive of projects?

We mentored two data science researchers in the last year of undergraduate study in statistics at University of Wisconsin-Madison. Both students developed novel research questions, collected observational data, analyzed data, and interpreted results.

- how did we balance our input with that of the students?
- What data did we use?
- How did we collect data? (which packages, code to sample twitter). How did Jinyu get her stock market data? 
- What is the sampling scheme - for the 1% sample - from the entirety of Twitter? (Cite the webpage that documents the API)

## Results

## Discussion

## References
